Generating Simulated Data

### 2021-04-06 docs/SimData.Rmd
initial length comps in model bins

@@

```{r lendat, eval=FALSE}
# rearrange into length bins and write length comp data csvs
#multiple surveys named in list object, use as filename
for(s in names(len_comp_data)){
  #arrange into long format: year, Species, agecl, length 
  svlenbin <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%

    tidyr::spread(lenbins, atoutput) %>%
    write_csv(paste0(o.name,"observation_lengths_NOBA_",s,".csv"))
}

>>>>

Note that spring surveys don't get mackerel at all (not in the model domain then). A full set of von B parameters could only be estimated for the first era of both versions of the fall survey tested here.

@@

```{r lendat, eval=FALSE}
# rearrange into length bins and write length comp data csvs
# modbins from sizebins above, differ by species so need modbin.min and modbin.max
# pcumsum is an FSA function

modbins <- sizebins %>%
  rename(species = `commentField-notused`) %>%
  pivot_longer(!species, names_to = "sizebin", values_to = "binwidth") %>%
  group_by(species) %>%
  arrange(sizebin) %>%
  mutate(modbin.min = pcumsum(binwidth),
         modbin.max = cumsum(binwidth)) %>%
  arrange(species, sizebin)

#multiple surveys named in list object, use as filename
for(s in names(len_comp_data)){
  #arrange into long format: year, Species, agecl, length 
  svlenbin <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%
    dplyr::left_join(modbins) %>%
    dplyr::filter(modbin.min < upper.bins & upper.bins <= modbin.max) %>%
    dplyr::group_by(species, year, sizebin) %>%
    dplyr::summarise(sumlen = sum(atoutput)) %>%
    tidyr::spread(sizebin, sumlen) %>%
    write_csv(paste0(o.name,"observation_lengths_NOBA_",s,".csv"))
}
